Hydras \& Co.

### 2022-03-12 doc/hydras.tex
re-reading pages 9-21

\subsection{Active links}
The  links which appear in this pdf  document lead are of three possible kinds of destination:
\begin{itemize}
\item Local links to the document itself,
\item External links, mainly to \coq's website,
\item Local links to pages generated by \texttt{coqdoc}. According to the current makefile (through the commands \texttt{make html} and \texttt{make pdf}), 
  we assume that the page generated from a library \texttt{XXX/YYY.v} is stored as
the relative address \texttt{../theories/html/hydras.XXX.YYY.html} (from the location of the pdf)
Thus,  active links to our \coq{} modules may be incorrect if you did not get this \texttt{pdf} document by compiling the distribution available at
\url{https://github.com/coq-community/hydra-battles}.

>>>>

\subsection{Active links}
The  links which appear in this pdf  document lead are of three possible kinds of destination:
\begin{itemize}
\item Local links to the document itself,
\item External links, mainly to \coq's website,
\item Local links to pages generated by \texttt{coqdoc}. According to the current makefile (through the commands \texttt{make html} and \texttt{make pdf}), 
  the pages generated by \texttt{coqdoc} are stored at 
the relative address \texttt{../theories/html/*.html} (from the location of the pdf).
Thus,  active links to our \coq{} modules may be incorrect if you did not get this \texttt{pdf} document by compiling the distribution available at
\url{https://github.com/coq-community/hydra-battles}.
